### 2021-05-19 article/article.tex
update

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Within the dotted (dashed) boundaries, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
   a dashed region is omitted in the left panel.}\label{fig:flux_ratio}
\end{figure}%TODO: fix cbar need high emt and log to show both cascade and track features at the same time.
%otherwise, the cascade ratio overpowers the track one.

@@

\begin{figure}
   \begin{center}
      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters other than the one shown are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately.}\label{fig:joint_3D}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
   \end{center}
\end{figure}
%TODO: dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?

@@

{\renewcommand{\arraystretch}{1.3}
 \begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{IceCube}  \\
      $\emt$ & [-0.0098, 0.009 ] & [-0.0148, 0.014 ] & [-0.0152, 0.0145] & [-, -] \\\\
      & \multicolumn{4}{c}{DeepCore}\\ [0.3em]
      $\ett$ & [-0.029, 0.045] & [-, -]& [-0.029, 0.045] & [-, -] \\
      $\emt$ & [-0.015, 0.0048] & [-, 0.015]& [-0.015, 0.0048] & [-, 0.015] \\
      $\eem$ & [-0.072, 0.075] & [-0.132, 0.127]& [-0.072, 0.075] & [-0.132, 0.127]\\
      $\eet$ & [-0.074, 0.141] & [-0.174, 0.20  ]& [-0.074, 0.141] & [-0.174, 0.20  ]\\\\
      &\multicolumn{4}{c}{IceCube + DeepCore}\\
      $\emt$ & [-0.0182,  0.00030] & [-, 0.0104] & [-0.0185, 0.00030] & [-, 0.0104] \\
      \hline
      \hline
   \end{tabular}
   \end{center}
   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst-case refers to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
\end{table}
\begin{table}
   \begin{tabular}{lcccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{PINGU} \\
      $\ett$ & [-0.0326, -] & [-0.0482, -] & [-0.0371, -] & [-, -] \\
      $\emt$ & [-0.0065, 0.0071] & [-0.011, 0.013] & [-0.0078, 0.0087] & [-0.0136, 0.0162] \\
      $\eem$ & [-0.062, 0.057] & [-0.122, 0.103] & [-0.1057, 0.0799] & [-0.198, 0.141]\\
      $\eet$ & [-0.069, 0.077] & [-0.121, 0.133] & [-0.1072, 0.1022] & [-0.1805, 0.1633]\\\\
      & \multicolumn{4}{c}{DeepCore + PINGU} \\
      $\ett$ & [-0.028, 0.043] & [-0.043, -] & [-0.0285,  0.0423] & [-0.0447, -]\\
      $\emt$ & [-0.0067, 0.0049] & [-0.0109,  0.0101] & [-0.0049, 0.0086] & [-0.0098, 0.0146]\\
      $\eem$ & [-0.048, 0.048]  & [-0.090, 0.085] & [-0.0721, 0.0503] & [-0.1262, 0.0931]\\
      $\eet$ & [-0.053, 0.072]  & [-0.101, 0.118] & [-0.0901, 0.0624] & [-0.1491, 0.1168]\\\\
      & \multicolumn{4}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ & [-0.0088,  0.003 ] & [-0.0128, 0.0081] & [-0.01, 0.0028] & [-0.0145, 0.0087]\\
      \hline
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

@@

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.38\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.01$
    to the standard interaction count}\label{fig:event_pulls} 
\end{figure}%TODO: redo these with same emt as flux_ratio?

% \begin{figure}[b]
%    \begin{center}
%       \includegraphics[width=0.2\linewidth]{figures/joint_3D_NO.pdf}
%    \end{center}
%    \caption{Expected joint $\Delta \chi^2$ from Eq.~\ref{eq:joint_chisq} for normal ordering.}
%    \label{fig:joint_3D}
% \end{figure}
%TODO:  Discussion on impact of IC on chisq.?

>>>>

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Within the dotted (dashed) boundaries, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
   a dashed region is omitted in the left panel.}\label{fig:flux_ratio}
\end{figure}%TODO: make prettier cmap

@@

\begin{figure}
   \begin{center}
      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters other than the one shown are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
   \end{center}
\end{figure}
%TODO: dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?

@@

{\renewcommand{\arraystretch}{1.3}
 \begin{table}
   \begin{center}
   \begin{tabular}{lcccccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{6}{c}{IceCube}  \\
      $\epsilon_{\mu\tau}$  &   [-0.01, 0.009] &  [-0.015, 0.014] &  [-0.013, 0.012] &  [-0.019, 0.018] &  [-0.015, 0.014] &  [-0.022, 0.021] \\\\
      & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
      $\epsilon_{\tau\tau}$ &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] \\
      $\epsilon_{\mu\tau}$  &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] \\
      $\epsilon_{e\mu}$     &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] \\
      $\epsilon_{e\tau}$    &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] \\\\
      &\multicolumn{6}{c}{IceCube + DeepCore}\\
      $\epsilon_{\mu\tau}$  &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] \\
      \hline
      \hline
   \end{tabular}
   \end{center}
   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
\end{table}
\begin{table}
   \begin{tabular}{lcccccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{6}{c}{PINGU} \\
      $\epsilon_{\tau\tau}$ &  [-0.033, 0.057] &         [-0.048] &  [-0.034, 0.059] &         [-0.051] &  [-0.037, 0.062] &         [-0.055] \\
      $\epsilon_{\mu\tau}$  &  [-0.007, 0.007] &  [-0.011, 0.013] &  [-0.007, 0.008] &  [-0.012, 0.014] &  [-0.008, 0.009] &  [-0.014, 0.016] \\
      $\epsilon_{e\mu}$     &  [-0.062, 0.057] &  [-0.122, 0.104] &  [-0.081, 0.067] &   [-0.162, 0.12] &   [-0.106, 0.08] &  [-0.199, 0.141] \\
      $\epsilon_{e\tau}$    &   [-0.07, 0.077] &   [-0.12, 0.133] &  [-0.086, 0.089] &   [-0.15, 0.148] &  [-0.107, 0.102] &  [-0.182, 0.164] \\\\
      & \multicolumn{6}{c}{DeepCore + PINGU} \\
      $\epsilon_{\tau\tau}$ &   [-0.033, 0.05] &  [-0.048, 0.065] &  [-0.033, 0.052] &   [-0.05, 0.067] &  [-0.035, 0.051] &  [-0.052, 0.068] \\
      $\epsilon_{\mu\tau}$  &  [-0.007, 0.006] &  [-0.011, 0.012] &  [-0.007, 0.006] &  [-0.012, 0.012] &  [-0.004, 0.011] &   [-0.01, 0.017] \\
      $\epsilon_{e\mu}$     &  [-0.057, 0.052] &  [-0.107, 0.095] &   [-0.067, 0.06] &  [-0.127, 0.107] &  [-0.097, 0.056] &   [-0.165, 0.11] \\
      $\epsilon_{e\tau}$    &  [-0.063, 0.075] &  [-0.113, 0.128] &  [-0.074, 0.086] &  [-0.136, 0.142] &  [-0.115, 0.065] &  [-0.184, 0.131] \\\\
      & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
      $\epsilon_{\mu\tau}$  &  [-0.009, 0.004] &  [-0.013, 0.009] &  [-0.009, 0.004] &   [-0.014, 0.01] &  [-0.008, 0.007] &  [-0.012, 0.013] \\
      \hline
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

@@

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.38\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.01$
    to the standard interaction count}\label{fig:event_pulls} 
\end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better
